Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-07-03 snapshot_system/arch.tex
CDS->PDS for failover, updated figures

\item Each non-PDS snapshot store is divided into a set of containers and each of them is approximately 
1G bytes. The reason we divide the snapshot into containers is to simplify the compact process
conducted periodically.  There are chunks deleted without any reference from other snapshots
and to reclaim the space of these useless chunks, a compaction  routine can work on one container at a time
and copy used data chunks to another container.
	\begin{itemize}
	\item Each container is divided into a set of chunk data groups. Each group is composed of
	a set of data chunks and is the basic unit for the snapshot in data access and retrieval. 
	In writing a chunk group, data chunks in this group are compressed together and then stored. 
	When accessing a particular chunk, its chunk group is retrieved from the disk storage
	and uncompressed. Given the high spatial locality 
in snapshot data accessing~\cite{Sampling,FoundationPaper},
	retrieval of  data chunks by group naturally fits in the prefetching scheme  to speedup
	snapshot access. A  typical chunk group contains 100 to 1000 chunks, with an average size of 
200-600KB.
Chunk grouping also reduces the  container index size as we discuss below. 
Given  the average chunk size  4KB,  the index size for a 1GB container reduces from 10MB to 100KB when
the chunk group size is 100.
%%CBlock, then the overall index size is reduced to $1/m$. 
%n our implementation, using $m=100$ reduces the index for
%a 1GB container from 10 MB to 100 KB.
	\item 
Each data container is represented by three data files in the DFS:
1) the container data file holds the actual content of data chunks, 
2) the container index file is responsible for translating a data reference
into its location within a container, and 
3) a chunk deletion log file saving all the deletion requests within  the container.
A VM snapshot store typically has a small number of containers because each container is fairly large with an average size of 1GB bytes, it 
maintains a limited number of snapshots (e.g. 10 in the Alibaba case),
and new snapshot data chunks can be effectively compressed in chunk groups in addition to  deduplication.

>>>>

\item Each non-PDS snapshot store is divided into a set of containers and each of them is approximately 
1GB. The reason we divide the snapshot into containers is to simplify the compact process
conducted periodically.  There are chunks deleted without any reference from other snapshots
and to reclaim the space of these useless chunks, a compaction  routine can work on one container at a time
and copy used data chunks to another container.
	\begin{itemize}
	\item Each container is divided into a set of chunk data groups. Each group is composed of
	a set of data chunks and is the basic unit for the snapshot in data access and retrieval. 
	In writing a chunk group, data chunks in this group are compressed together and then stored. 
	When accessing a particular chunk, its chunk group is retrieved from the disk storage
	and uncompressed. Given the high spatial locality 
in snapshot data accessing~\cite{Sampling,FoundationPaper},
	retrieval of  data chunks by group naturally fits in the prefetching scheme  to speedup
	snapshot access. A  typical chunk group contains 100 to 1000 chunks, with an average size of 
200-600KB.
Chunk grouping also reduces the  container index size as we discuss below. 
Given  the average chunk size  4KB,  the index size for a 1GB container reduces from 10MB to 100KB when
the chunk group size is 100.
%%CBlock, then the overall index size is reduced to $1/m$. 
%n our implementation, using $m=100$ reduces the index for
%a 1GB container from 10 MB to 100 KB.
	\item 
Each data container is represented by three data files in the DFS:
1) the container data file holds the actual content of data chunks, 
2) the container index file is responsible for translating a data reference
into its location within a container, and 
3) a chunk deletion log file saving all the deletion requests within  the container.
A VM snapshot store typically has a small number of containers because each container is fairly large with an average size of 1GB, it 
maintains a limited number of snapshots (e.g. 10 in the Alibaba case),
and new snapshot data chunks can be effectively compressed in chunk groups in addition to  deduplication.

### 2013-07-03 snapshot_system/failover.tex
CDS->PDS for failover, updated figures

The replication degree of the backup storage 
is $r$ for regular file blocks and $r=3$ is a typical setting in the distributed
file system~\cite{Hadoop,GFS}.
In the VC approach, a special replica degree $r_c$ used for CDS blocks where $r_c>r$. 
Notice that the ratio of non CSD data size vs CDS data size for each VM is
\[
\sigma=  \frac{c*\delta(1 -   (\frac{k}{c_u})^{1-\alpha})} {k}.
\]

@@

In our experiment with Alibaba data, the ratio $\sigma$ 
is 162. Thus allocation of extra replicas for CDS only introduces a small amount of extra space
cost.  Figure~\ref{fig:storageCDS} shows the storage cost ratio of VC and VO when 
$r$=3, and $r_c$ varies from 3 to 10.
The result shows that the storage cost for adding extra replication for CDS
is insignificant.

@@

Next we discuss how a failure of $d$ machines impacts the VM snapshots in VC.
When $d<r$, there is no loss of data in the snapshot storage.
When $r_c> d \ge r$, some of data blocks in the storage are lost, and we compute the number of VMs that could
suffer the loss of their snapshots.
When $d \ge r_c$, some of CDS blocks are affected.
In VC, the blocks in CDS are stored in a container manner (superblock), and they are shared by many VMs.
The number of data containers stored with replication degree $r$ for
referenced by each VM is:
\[
N_1= \frac{b}{v*s} (1-\delta) +b/(v*s)\delta (1 -  (\frac{k}{b_u})^{1-\alpha}).
\]
The number of CDS data containers stored with replication degree $r_c$ for
referenced by each VM is:
\[
N_2= \frac{b}{v*s}\delta (\frac{k}{b_u})^{1-\alpha}.
\]
}

@@

To  compute the probablity of losing snapshots of a virtual machine, 
we estimate the number of file system blocks per VM in each apporach.
We can build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs. An association edge is  drawn  from a file block  to a VM 
if this file is used by this VM. 
For VC, each VM has an 
averge number of $N_1$ file system blocks for non-CDS data. 
It also refers  an average of   $N_2$ file system blocks for CDS data 
For VO, each VM has an average  of  $N_o$ file system blocks
and let $V_o$ be the averge number of VMs shared by each file system block.
Figure~\ref{fig:shared} illustates the bipartite association.

In VC, each non-CDS file system block is associated with one VM while CDS file system blocks are
shared among VMs  (at most $V$ VMs). Thus, 
\[
V *N_1 *s  = pD  \frac{\delta} {\delta +1} \; \mbox{ and } \; 
V *N_2 *s  \leq pD  \frac{1} {\delta +1} *V.
\]
For the VO approach, 
\[
V *N_o *s  = pD  V_o.
\]
Then
\[
N_1= \frac{pD \delta} {V s (\delta +1)},\; 
N_2 \leq \frac{pD } {s (\delta +1)}, \; 
\mbox{and} \; N_o = \frac{pD V_o } {s V}.
\]
Since each file block (with default size $s=64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.
Figure~\ref{fig:VOshared} shows the number of VMs shared by each file block.
In our experiment, we find that $V_o \approx 0.2 V$ when backing up VMs one by one.
We can observe that $N_1 +N_2 << N_o$.
If  the backup for multiple VMs is conducted concurrently, there would be more
VMs shared  by each file block on average.

Figure~\ref{fig-vo-links} shows the average number of VMs sharing a block in
the global index as more VMs are added in VO. The first 15 VMs are all windows
machines in that plot, so that explains the initial higher values, but for the
most part the average number of links is between 1.5 and 2.
Figure~\ref{fig-vo-fsb-links} shows the average number of VMs sharing a
filesystem block (FSB) in the global index as VMs are added. Two of the VMs had
much larger hard drives (\~300GB), which explains the 2 drops, as those two VMs
added much more unique data than normal. You can see in the plot that even
though a FSB contains 16K chunks, the average number of links to an FSB is only
several times the number of average links to a chunk. This is because even in
the VO global deduplication model, as long as writes are batched a single FSB
will tend to contain chunks from only a small number of VMs. Below we show the
significant impact the number of links has on VM backup reliability.

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. links to a chunk},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a data chunk in the global index}
  \label{fig-vo-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Container links},
		xlabel={Number of VMs},
		ylabel={Avg. links to an FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		]
                \addplot[color=blue,mark=*] table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
                %\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB Filesystem Block in the global index (for VO)}
  \label{fig-vo-fsb-links}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Avg CDS Container Links},
		xlabel={Number of VMs},
		ylabel={Avg. links to CDS FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=cdslinks] {figures/cds_links.txt};
		%\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB CDS Filesystem Block for (VC with 5\% CDS)}
  \label{fig-cds-fsb-links}
\end{figure}

@@

When there are $r \le d<r_c$ machines failed and then there is no CDS data loss,  
%a file block failure depends on if all replicas of this container reside in the failed machines.
the snapshot avaiability of a VM in the VC approach is 
and is
\[
(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
\]
%\begin{multline}
%= Probability (\mbox{ There is no file block loss in this VM}) \\
%= Probability(\mbox{ A file block has file data loss})^{N_1}\\
%= (1- Probability (\mbox{all replicas of its block fail}))^{N_1}\\
%\end{multline}
%\end{split}

When $r_c \leq d$, both non-CDS and CDS file blocks in VC can have a loss.
The snapshot availability of  a VM in the VC approach is
\[
(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
*
(1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
\]
%= Probability(\mbox{ No non-CDS file block loss})^{N_1}
%Probability(\mbox{ No CDS file block loss})^{N_2}\\
%\begin{multline}
%\end{split}
%\end{multline}

@@

Since both in the CDS and in the VO approach a single filesystem chunk may be used by many VMs,
we must multiply the block failure ratio by the number of outgoing links for the block to get
the expected impact on the system.
\[
    E_{VMfailure}=L\frac{\binom{d}{r}}{\binom{p}{r}}
\]

in our current testbed we have measured the average number of links per block
(Figure~\ref{vo-links}) and number of links per chunk
(Figure~\ref{fig-vo-fsb-links}) in our dataset. For the complete dataset, we
also found the average number of links to CDS chunks, which was 11 using a 5\%
CDS. From Figure~\ref{fig-vo-fsb-links} you can see that as you add VMs, the
average number of links to a chunk increases linearly for our dataset. We
expect that this trend will level out with larger datasets, but should continue
to increase at a slower rate.  For the VC model, we have to consider both CDS
chunks and Non-CDS chunks. In the VO model all data is shared, but in VC only
the CDS data is shared, but at a much higher rate. This gives a strong
advantage to VC, in that for a large percent of the data (95-99\%), there is
only one VM pointing to each Non-CDS chunk. You can see the increase in
reliability in Figure~\ref{fig-vm-availability}.
}

Figure~\ref{fig-vm-availability} shows the reliability of VM backups as storage
nodes fail for different numbers of links to average blocks in the index. We
chose 5 and 11 for the VO and VC block links counts because those are what we
measured in our dataset, and chose higher numbers to account for much larger
datasets. As you can see from the graph, even small changes in the number of
links to VO blocks has a significant impact on reliability, while even a 100
times increase in the VC block link counts only slightly affects VC
reliability.  The key factor placed is that  $N_1 +N_2 << N_o$, caused by the
fact that the VM-centric approach localizes deduplication and packs  data
blocks for one VM as much as possible.  The extra replicaton for CDS blocks
also signficantly increaes the snapshot availability even when a CDS file block
is shared by every VM.

% while in VO even small increases in $L$ causes a large decrease in availability. 
Figure~\ref{fig-cds-replication}
shows the advantages of increasing the replication factor for CDS blocks. the
numbers in the graph are only meant to be relative, as we assume higher CDS
block links than we have measured in our dataset (to account for a much larger
body of data). It is easy to see though that increasing the replication of just
the CDS blocks (which are the most popular blocks) can have a positive impact
on the overall reliablity of the VM backups. These figures together show the
advantages of the VM-centric model, and the advantages that separating the
replication factor for popular blocks can have on reliability.

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
            \legend{$VO\,10$,$VO\,5$,$VC\,1000$,$VC\,11$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for varying average block link counts (i.e. average number of VMs that use a block)}
  \label{fig-vm-availability}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={CDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot[color=brown,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                \addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
            \legend{$R_C=3$,$R_C=4$,$R_C=5$,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different CDS Replication factors (Non-CDS replication fixed at 3, and average CDS block links set to 1000)}
  \label{fig-cds-replication}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\comments{
We use the following parameters  during the analysis
\begin{itemize}
\item 	$V$ is the number of VMs. $m$ is the number of physical machines hosting the backup storage.
$d$ is the number of machines failed.
\item In the VC approach, $s_c$  of them in the backup storage
are shared by others with a zipf distribution. $(1-s_c)$ 
of them  is unique (nobody shares with them).
$L_c$ is the average number of VMs sharing a block (if it is in CDS for the VC approach.
$b_c$ is the number of shared blocks in VC.
\item In the VO approach, $s_o$ is the number of blocks shared.
$L_o$ is the average number of VMs sharing a block. 
\item $b$ is the  number of blocks stored in the storage after deduplication.
 \end{itemize}

@@

\subsubsection{CDS and Fault Tolerance}
%all numbers in this paragraph need to be corrected after I re-run the tests
%using the actual cds generator code
As part of our emprirical validation of our model, we also computed the effects
of the CDS on fault tolerance. If we exclude the top 5\% most popular blocks
and set aside those in the CDS, the average number of links to a non-CDS block
%TODO: insert figure generated from data/links_cds.dat and data/links_wo_cds.dat
drops to 10.3 for 350 snapshots. This means that on average, \~3 fewer
snapshots will be affected by a lost data block in the general data store.
The average number of links to a CDS block however, for 350 snapshots, is
65.7. This suggests that a much higher replication factor is warranted for
the CDS, as on average, a CDS block appears in \~20\% of all the snapshots.
These measured numbers are different from our theoritical model due to the fact
that duplicate data blocks are not uniformly distributed across all VMs.
With uniform distribution of duplicates (and a zipf distribution on the number
of duplicates), there should be on average 2.55 incoming VM links to each
block. Since we show the average number of links to be 1.47 in our actual
traces, the duplicates are
more tighly grouped than the uniform model would predict. This supports
the benefits of using a CDS plus more localized deduplication.

The CDS gives a clear boundary for setting different replication factors,
And our tests suggest that by separating the replication factor for the CDS
and non-CDS blocks, greater fault tolerance can be acheived.

@@

For CDS model, 85% blocks are using the data from the same VM while upto 10% data is for CDS (we actually only use 5% perhaps).  Thus the overall speaking, at most 10% of data are shared.
Thus  for CDS approach,   the # VM failure caused by k machines is at most  [ 1-  C(r, k) /C(n,r)] * b* [ 1+ 0.10 *V(1-1/ln V)].
For original approach,  [ 1-  C(r, k) /C(n,r)] * b* [ 1+ 0.90 *V(1-1/ln V)].
For large V, the reliability improves by 9 times.
}

>>>>

The replication degree of the backup storage 
is $r$ for regular file blocks and $r=3$ is a typical setting in the distributed
file system~\cite{Hadoop,GFS}.
In the VC approach, a special replica degree $r_c$ used for PDS blocks where $r_c>r$. 
Notice that the ratio of non-PDS data size vs PDS data size for each VM is
\[
\sigma=  \frac{c*\delta(1 -   (\frac{k}{c_u})^{1-\alpha})} {k}.
\]

@@

In our experiment with Alibaba data, the ratio $\sigma$ 
is 162. Thus allocation of extra replicas for PDS only introduces a small amount of extra space
cost.  Figure~\ref{fig:storageCDS} shows the storage cost ratio of VC and VO when 
$r$=3, and $r_c$ varies from 3 to 10.
The result shows that the storage cost for adding extra replication for PDS
is insignificant.

@@

Next we discuss how a failure of $d$ machines impacts the VM snapshots in VC.
When $d<r$, there is no loss of data in the snapshot storage.
When $r_c> d \ge r$, some of data blocks in the storage are lost, and we compute the number of VMs that could
suffer the loss of their snapshots.
When $d \ge r_c$, some of PDS blocks are affected.
In VC, the blocks in PDS are stored in a container manner (superblock), and they are shared by many VMs.
The number of data containers stored with replication degree $r$ for
referenced by each VM is:
\[
N_1= \frac{b}{v*s} (1-\delta) +b/(v*s)\delta (1 -  (\frac{k}{b_u})^{1-\alpha}).
\]
The number of PDS data containers stored with replication degree $r_c$ for
referenced by each VM is:
\[
N_2= \frac{b}{v*s}\delta (\frac{k}{b_u})^{1-\alpha}.
\]
}

@@

To  compute the probablity of losing snapshots of a virtual machine, 
we estimate the number of file system blocks per VM in each apporach.
We can build a bipartite graph representing the association from unique file system blocks
to their corresponding VMs. An association edge is  drawn  from a file block  to a VM 
if this file is used by this VM. 
For VC, each VM has an 
averge number of $N_1$ file system blocks for non-PDS data. 
It also refers  an average of   $N_2$ file system blocks for PDS data 
For VO, each VM has an average  of  $N_o$ file system blocks
and let $V_o$ be the averge number of VMs shared by each file system block.
Figure~\ref{fig:shared} illustates the bipartite association.

In VC, each non-PDS file system block is associated with one VM while PDS file system blocks are
shared among VMs  (at most $V$ VMs). Thus, 
\[
V *N_1 *s  = pD  \frac{\delta} {\delta +1} \; \mbox{ and } \; 
V *N_2 *s  \leq pD  \frac{1} {\delta +1} *V.
\]
For the VO approach, 
\[
V *N_o *s  = pD  V_o.
\]
Then
\[
N_1= \frac{pD \delta} {V s (\delta +1)},\; 
N_2 \leq \frac{pD } {s (\delta +1)}, \; 
\mbox{and} \; N_o = \frac{pD V_o } {s V}.
\]
Since each file block (with default size $s=64MB$) contains many chunks (on average 4KB),
each file block contains the hot low-level chunks shared by many VMs, and it also contains
rare chunks which are not shared.
Figure~\ref{fig:VOshared} shows the number of VMs shared by each file block.
In our experiment, we find that $V_o \approx 0.2 V$ when backing up VMs one by one.
We can observe that $N_1 +N_2 << N_o$.
If  the backup for multiple VMs is conducted concurrently, there would be more
VMs shared  by each file block on average.

Figure~\ref{fig-fsb-links} shows the average number of VMs sharing a
filesystem block (FSB) in the global index as VMs are added. Two of the VMs had
much larger hard drives (\~300GB), which explains the 2 drops, as those two VMs
added much more unique data than normal. Though we expect the graph to level out some for
much larger datasets, it should continue to increase, which has important implications
on VM backup availability in the precense of failures. Below we show the
significant impact the number of links has on VM backup reliability.

\comments{%dropping block links bec. we don't use it elsewhere
\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Block links},
		xlabel={Number of VMs added},
		ylabel={Avg. links to a chunk},
		%extra y ticks={4.5,5.5,6.5} %because it only shows 4,5,6,7
		legend pos=south east
		]
		\addplot[color=blue,mark=*] table[x=VMs,y=Measured] {figures/vo_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=Theoretical] {figures/vo_links.txt};
		\legend{Measured,Theoretical};
		\end{axis}
	\end{tikzpicture}
  \caption{Average number of VMs sharing a data chunk in the global index}
  \label{fig-vo-links}
\end{figure}
}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={VO Container links},
		xlabel={Number of VMs},
		ylabel={Avg. Num. VMs sharing FSB},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		legend pos=south east
		]
                \addplot[color=blue,mark=*] table[x=VMs,y=FSBLinks] {figures/vo_fsb_links.txt};
		\addplot[color=red,mark=square*] table[x=VMs,y=cdslinks] {figures/cds_links.txt};
                \legend{Global Dedup (VO), PDS FSB (VC)};
		\end{axis}
	\end{tikzpicture}
  \caption{Measured Average number of VMs sharing a 64MB FSB with global dedup (VO), and in the PDS for VC.}
  \label{fig-fsb-links}
\end{figure}

@@

When there are $r \le d<r_c$ machines failed and then there is no PDS data loss,  
%a file block failure depends on if all replicas of this container reside in the failed machines.
the snapshot avaiability of a VM in the VC approach is 
and is
\[
(1-\frac{\binom{d}{r}} { \binom{p}{r} })^{N_1}.
\]
%\begin{multline}
%= Probability (\mbox{ There is no file block loss in this VM}) \\
%= Probability(\mbox{ A file block has file data loss})^{N_1}\\
%= (1- Probability (\mbox{all replicas of its block fail}))^{N_1}\\
%\end{multline}
%\end{split}

When $r_c \leq d$, both non-PDS and PDS file blocks in VC can have a loss.
The snapshot availability of  a VM in the VC approach is
\[
(1-\frac{ \binom{d}{r}} { \binom{p}{r} })^{N_1} 
*
(1-\frac{ \binom{d}{r_c}} { \binom{p}{r_c} })^{N_2}.
\]
%= Probability(\mbox{ No non-PDS file block loss})^{N_1}
%Probability(\mbox{ No PDS file block loss})^{N_2}\\
%\begin{multline}
%\end{split}
%\end{multline}

@@

Since both in the PDS and in the VO approach a single filesystem chunk may be used by many VMs,
we must multiply the block failure ratio by the number of outgoing links for the block to get
the expected impact on the system.
\[
    E_{VMfailure}=L\frac{\binom{d}{r}}{\binom{p}{r}}
\]

in our current testbed we have measured the average number of links per chunk
(Figure~\ref{vo-links}) and number of links per Filesystem Block (FSB)
(Figure~\ref{fig-fsb-links}) in our dataset. For the complete dataset, we
also found the average number of links to PDS chunks, which was 11 using a 5\%
PDS. From Figure~\ref{fig-fsb-links} you can see that as you add VMs, the
average number of links to a chunk increases linearly for our dataset. We
expect that this trend will level out with larger datasets, but should continue
to increase at a slower rate.  For the VC model, we have to consider both PDS
chunks and non-PDS chunks. In the VO model all data is shared, but in VC only
the PDS data is shared, but at a much higher rate. This gives a strong
advantage to VC, in that for a large percent of the data (95-99\%), there is
only one VM pointing to each non-PDS chunk. You can see the increase in
reliability in Figure~\ref{fig-vm-availability}.
}

Figure~\ref{fig-vm-availability} shows the reliability of VM backups as storage
nodes fail for different numbers of links to average blocks in the index. We
chose 5 and 11 for the VO and VC block links counts because those are what we
measured in our dataset, and chose higher numbers to account for much larger
datasets. We chose to use a very optimistic setting for VO (10), and an extreme
amount of sharing for VC (1000) to better show the significant improvement in
data reliability for the VC model. As you can see from the graph, even small
changes in the number of links to VO blocks has a significant impact on
reliability, while even a 100 times increase in the VC block link counts only
slightly affects VC reliability.  The key factor placed is that  $N_1 +N_2 <<
N_o$, caused by the fact that the VM-centric approach localizes deduplication
and packs  data blocks for one VM as much as possible.  The extra replicaton
for PDS blocks also signficantly increases the snapshot availability even when
a PDS file block is shared by every VM.

% while in VO even small increases in $L$ causes a large decrease in availability. 
Figure~\ref{fig-pds-replication}
shows the advantages of increasing the replication factor for PDS blocks. the
numbers in the graph are only meant to be relative, as we assume higher PDS
block links than we have measured in our dataset (to account for a much larger
body of data). It is easy to see though that increasing the replication of just
the PDS blocks (which are the most popular blocks) can have a positive impact
on the overall reliablity of the VM backups. These figures together show the
advantages of the VM-centric model, and the advantages that separating the
replication factor for popular blocks can have on reliability.

\begin{figure}[ht]
  \centering
  %\includegraphics[scale=.45,natwidth=511,natheight=276]{vo_links}
	\begin{tikzpicture}
		\begin{axis}[
		%title={Node failure affect on VMs},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[densely dashed,color=blue,mark=square*] table[x=NodesFailed,y=VO2]{figures/vm_failure_2.txt};
                \addplot[densely dashed,color=blue,mark=*] table[x=NodesFailed,y=VO1]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=triangle*,mark size=3] table[x=NodesFailed,y=VO3]{figures/vm_failure_2.txt};
                %\addplot[densely dashed,color=blue,mark=diamond*,mark size=3] table[x=NodesFailed,y=VO4]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/vm_failure_2.txt};
                \addplot[color=red,mark=*] table[x=NodesFailed,y=VC1]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/vm_failure_2.txt};
                %\addplot[color=red,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/vm_failure_2.txt};
            \legend{$VO\,10$ (optimistic),$VO\,5$ (measured),$VC\,1000$ (extreme),$VC\,11$ (measured)}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail for VO and VC models for varying average block link counts (i.e. average number of VMs that use a block). Non-PDS replication fixed at 3 and PDS replication increased to 4.}
  \label{fig-vm-availability}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
		extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                }
		]
                \addplot[color=blue,mark=*] table[x=NodesFailed,y=VC1]{figures/cds_replication.txt};
                \addplot[color=red,mark=square*] table[x=NodesFailed,y=VC2]{figures/cds_replication.txt};
                \addplot[color=brown,mark=triangle*,mark size=3] table[x=NodesFailed,y=VC3]{figures/cds_replication.txt};
                \addplot[color=black,mark=diamond*,mark size=3] table[x=NodesFailed,y=VC4]{figures/cds_replication.txt};
            \legend{$R_C=3$,$R_C=4$,$R_C=5$,$R_C=7$}
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM backups as nodes fail in the VC model for different PDS Replication factors (Non-PDS replication fixed at 3, and average PDS block links set to 1000)}
  \label{fig-pds-replication}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%NEW MODEL END%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\comments{
We use the following parameters  during the analysis
\begin{itemize}
\item 	$V$ is the number of VMs. $m$ is the number of physical machines hosting the backup storage.
$d$ is the number of machines failed.
\item In the VC approach, $s_c$  of them in the backup storage
are shared by others with a zipf distribution. $(1-s_c)$ 
of them  is unique (nobody shares with them).
$L_c$ is the average number of VMs sharing a block (if it is in PDS for the VC approach.
$b_c$ is the number of shared blocks in VC.
\item In the VO approach, $s_o$ is the number of blocks shared.
$L_o$ is the average number of VMs sharing a block. 
\item $b$ is the  number of blocks stored in the storage after deduplication.
 \end{itemize}

@@

\subsubsection{PDS and Fault Tolerance}
%all numbers in this paragraph need to be corrected after I re-run the tests
%using the actual cds generator code
As part of our emprirical validation of our model, we also computed the effects
of the PDS on fault tolerance. If we exclude the top 5\% most popular blocks
and set aside those in the PDS, the average number of links to a non-PDS block
%TODO: insert figure generated from data/links_cds.dat and data/links_wo_cds.dat
drops to 10.3 for 350 snapshots. This means that on average, \~3 fewer
snapshots will be affected by a lost data block in the general data store.
The average number of links to a PDS block however, for 350 snapshots, is
65.7. This suggests that a much higher replication factor is warranted for
the PDS, as on average, a PDS block appears in \~20\% of all the snapshots.
These measured numbers are different from our theoritical model due to the fact
that duplicate data blocks are not uniformly distributed across all VMs.
With uniform distribution of duplicates (and a zipf distribution on the number
of duplicates), there should be on average 2.55 incoming VM links to each
block. Since we show the average number of links to be 1.47 in our actual
traces, the duplicates are
more tighly grouped than the uniform model would predict. This supports
the benefits of using a PDS plus more localized deduplication.

The PDS gives a clear boundary for setting different replication factors,
And our tests suggest that by separating the replication factor for the PDS
and non-PDS blocks, greater fault tolerance can be acheived.

@@

For PDS model, 85\% blocks are using the data from the same VM while upto 10\% data is for PDS (we actually only use 5% perhaps).  Thus the overall speaking, at most 10% of data are shared.
Thus  for PDS approach,   the # VM failure caused by k machines is at most  [ 1-  C(r, k) /C(n,r)] * b* [ 1+ 0.10 *V(1-1/ln V)].
For original approach,  [ 1-  C(r, k) /C(n,r)] * b* [ 1+ 0.90 *V(1-1/ln V)].
For large V, the reliability improves by 9 times.
}
